SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-27 paper.tex
minor changes

%--------------------------------------
\section{Achievements and Future Trends}
\label{achievements}
%--------------------------------------

@@

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated in the literature, which demonstrate its effectiveness in some real-life embedded-systems applications~\cite{Gadelha15,Brain15,Rocha15}; however, the main challenge still remains open, {\it i.e.}, to compute and strengthen loop invariants to prove program correctness and timeliness in a more efficient and effective way, in order to be competitive with other model-checking approaches. In particular, invariant-generation algorithms have substantially evolved over the last years to discover inductive invariants of programs~\cite{pips:2013,Henry:2012} or to continuously refine them during verification~\cite{Beyer15}. However, there is still a lack of studies for exploiting the combination of different invariant-generation algorithms ({\it e.g.}, interval analysis, linear inequalities, polynomial equalities and inequalities) and how to strengthen them during verification, in order to ensure system robustness w.r.t. implementation aspects.

@@

\textcolor{red}{to pensando se o Qt nao pode ser descrito como um esforco de prover verificadores para interfaces diferentes}

>>>>

%--------------------------------------
\section{Current Achievements and Future Trends}
\label{achievements}
%--------------------------------------

@@

\textbf{(RP3)} Novel approaches to model check embedded software using \textit{k}-induction and invariants were proposed and evaluated in the literature, which demonstrate its effectiveness in some real-life embedded-systems applications~\cite{Gadelha15,Brain15,Rocha15,Donaldson10}; however, the main challenge still remains open, {\it i.e.}, to compute and strengthen loop invariants to prove program correctness and timeliness in a more efficient and effective way, in order to be competitive with other model-checking approaches. In particular, invariant-generation algorithms have substantially evolved over the last years to discover inductive invariants of programs~\cite{pips:2013,Henry:2012} or to continuously refine them during verification~\cite{Beyer15}. However, there is still a lack of studies for exploiting the combination of different invariant-generation algorithms ({\it e.g.}, interval analysis, linear inequalities, polynomial equalities and inequalities) and how to strengthen them during verification, in order to ensure system robustness w.r.t. implementation aspects.

@@

%\textcolor{red}{to pensando se o Qt nao pode ser descrito como um esforco de prover verificadores para interfaces diferentes}
